% lithium ion: lithium cobalt oxide / graphite
% 0.30 mAh
\chapter{Experimental Procedure}
The goal of the first experiment was to acoustically observe cycling-induced lithium plating using ToF data. It was unsuccessful due to overwhelming noise due to uncontrolled ambient conditions. In response, several improvements were made to the experimental apparatus in an attempt to eliminate appreciable noise in the ToF data due to ambient conditions. The second experiment's goal was to determine whether these changes adequately controlled the ambient conditions to prevent them from overwhelming the ToF data with noise; it was successful. The experiment showed a close and consistent relationship between time of flight and cell state of charge (ToF and SoC).

Recall that three three main determinants of change in acoustic wave time of flight through a battery cell are thought to be ambient conditions (most relevantly, temperature and pressure), state of charge, and state of health. Now that the set-up was validated to have minimal change in ambient conditions, and a relationship between ToF and SoC strongly established, further experimentation could reasonably explore the relationship between the cell's state of health and acoustic time of flight. The goal of the third experiment was to force plating via purposefully reckless electrochemical cycling, and acoustically observe this while it happens using ToF data; it was successful. The goal of the fourth experiment was to establish how reckless cycling would need to be in order to induce plating, by cycling at 5C but never 10C rates of charge; the 5C charge cycles were found to induce little plating \todo{discuss temps}. The goal of the fifth experiment was then to induce just some plating in the cell, by loading at a 10C charge rate for only one charging cycle; it was successful. Then, the goal of the sixth experiment was to establish a baseline for the ToF data without any plating by repeatedly (20 times) loading a cell at a very low rate of charge (C/2.5) to better understand the acoustic ToF response when no appreciable plating occurs.

\section{Observing ToF Shifts Due to State of Charge}

\subsection{Acoustic Monitoring of Cell Cycling in Unsteady Conditions}

The cell was cycled (charged and discharged) five times at a C/2.5 rate. 
Both the battery cell and the transducers used to send and receive the acoustic waves are subject to changes in operating characteristics due to change in temperature, so each testing protocol begins with a long rest to give the unit under test and the testing equipment time to acclimate to the ambient conditions. 
Then, the cell charges at a constant-current rate of 0.0120 Amps. 
The C/2.5 rate was chosen because such a gentle rate would induce very little lithium plating, and state of health of the cell would be roughly constant. 
If the cell's state of health did not change between cycles, and the experiment's ambient conditions held steady, then all changes in acoustic time of flight can be assumed to be due to change in state of charge.
The cycle then rested ten minutes, was discharged using the same constant-current, C/2.5 protocol, and then rested for ten minutes again. 
The rests between and within cycles allow for the cell to reach new steady-state conditions. 
There was a potential for the cell to experience somewhat significant transient effects due to phenomena such as the heat addition or structural stiffening during the oxidation-reduction reaction of cyclic charging and discharging; the rest cycles give the cell time to relax and modulate.
Then, the rest-charge-rest-discharge sequence was repeated for a total of five cycles.

\todo{insert flowchart}

Unfortunately, the assumption that the ambient conditions were steady did not hold, leading to considerable noise in the in the readings due to environmental interference, ultimately drowning the acoustic ToF signal. At that point, the exact source of the noise was unknown.

\todo{insert plots?}
    
\subsection{Acoustic Monitoring of Cell at Rest in Unsteady Conditions}\label{chamberTest}
Since it was impossible to determine the source of changes in ToF data for the prior test, or to determine what was signal and what was noise, a more piecewise approach to building up the experiment was needed. Due to the very small size of the cell, small variations in temperature and pressure could theoretically have relatively large impacts on the speed with which high-frequency acoustic waves travel through the cell. Some possible solutions were identified as: regulating the temperature to be relatively constant, better regulating the pressure applied to the cell, and using higher frequency transducers to probe the cell. Switching the 2.5MHz transducers for 15MHz transducers was quick and easy since the second set of transducers was already on hand, so this was done for the next trial. Additionally, the relatively loosely fluctuating ambient temperature was expected to have a relatively large effect on time of flight, so the pressurizing apparatus was inserted into a thermal chamber, as described in \hyperref[thermalChamber]{\cref{thermalChamber}}. The stack pressure is expected to a small fraction of an MPa and expensive to change, so this was left unchanged, to be revisited only if necessary.

Additionally, the cycling was postponed to a later experiment.
For now, the cell would be left at rest for the duration of the experiment. 
If there was no significant shift in acoustic ToF data while the cell waited at rest for a long period, then the noise in the environment is adequately controlled and cycling experimentation can proceed. 
If there were still shifts, the environment would need further control, probably through higher-precision active temperature control and pressure control. 
For 24 hours, the cell was probed ultrasonically while pressurized in the thermal chamber \todo{thermal, pressure data}.

\todo{plots}
The data show that the ToF did not shift while the temperature was held constant, and then shifted in step with a shift in temperature at the end, verifying that this setup effectively reduced environmental noise to acceptable levels to begin attempting to observe ToF shifts due to cell state.

\subsection{Acoustic Monitoring of Cell Cycling in Steady Conditions}
\todo{plots?}
Once the noise levels were brought under control, attempting to observe change of state via acoustic ToF shift could begin. The cycle was set up as in the first experiment, with a long initial rest period to ensure starting conditions were steady state, then five cycles consisting of a 10 minute rest, a C/2.5 current-controlled charge, another 10 minute rest, and then a C/2.5 current-controlled discharge. 

The system was kept pressurized to 2.4 PSI, which was a stack pressure of about 0.42MPa, falling into Cannarella's low stack pressure regime.

\section{Observing ToF Shifts Due to State of Health} 
Once confirmed that the experimental set-up was capable of observing change of state of charge of the cell, it could be investigated whether it could observe changes in state of health.

\subsection{Acoustic Monitoring of Lithium Plating}
\todo{flowchart}
The battery was set-up in the pressurized, thermally-regulated apparatus as before; this time at a temperature of \todo{temp} C and a system pressurization of \todo{pres} psi, which applied a stack pressure of \todo{stack}. 
The cell was again cycled but this time with aggressive ramps in charging rate. 
This intentionally reckless operation would force significant lithium plating to develop on the anode. 
After a rest to ensure steady-state conditions, the cell was given a ten minutes rest, charged at a 1C rate for 60 minutes, given 10 minutes rest, and discharged at a C/2 rate. 
This sequence was repeated once, for two total cycles. 
It was then repeated with a charging protocol of 2C for 30 minutes, then 5C for 12 minutes, then 10C for 6 minutes. 
Lithium plating was expected to be observed in the latter two cycles.
\todo{plots?}


\subsection{Acoustic Monitoring of Lithium Unplating}
The goal of this test was to plate lithium at less aggressive charging rates of 5C, rather than 10C, so that most or all appreciable plating would be removed during the discharge cycle. XPS and SEM analysis showed this to be mostly successful \todo{moar}. However, the temperature fluctuated much more during this experiment than the prior, and this lead to noisy readings of time of flight. This was used as an opportunity to try to relate change in ambient temperature with change in time acoustic time of flight. The results of this analysis were \todo{do analysis}


\subsection{Acoustic Monitoring of a Minimum of Lithium Plating}
The goal of this experiment was to plate a fixed amount of lithium. It used a protocol similar to the earlier plating protocol, but with only one cycle of charging at the 10C rate. One hiccup during this experiment was that the thermocouples stopped logging data for most of the experiment. 


\section{Baseline Correlation Between ToF shifts and Acoustic Plating}
System pressurized to 3.7 psi, a stack pressure of 0.065 MPa (Cannarella's low stack pressure).